---
title: "R_PROJECT"
author: "DPLYR"
date: "2024-04-18"
output: 
    prettydoc::html_pretty:
     themes: leonids
---
**DPLYR Questions**

1.Return rows of cars that have an mpg value greater than 20 and 6 cylinders.
```{r}
library(dplyr)
```

```{r}
data(mtcars)
head(mtcars)
```

```{r}
cars =select(filter(mtcars,mpg>20,cyl==6),'mpg','cyl')
cars
```

2.Reorder the Data Frame by cyl first, then by descending wt.
```{r}
mtcars %>%
  arrange(cyl, desc(wt))
```

3.Select only the columns mpg and hp.
```{r}
select(mtcars,'mpg','hp')
```

4.Select the distinct values of the gear column.
```{r}
distinct(select(mtcars,gear))
```

5.Create a new column called “Performance” which is calculated by hp divided by wt.
```{r}
car =mutate(mtcars,Performance = hp / wt)
car
```

6.Find the mean mpg value using dplyr.
```{r}
summarise(mtcars,mean_mpg =mean(mpg))
```

7.Use pipe operators to get the mean hp value for cars with 6 cylinders.
```{r}
mtcars %>%
filter(cyl==6)  %>%
 summarise(mean_hp =mean(hp))
```

