---
title: "R_PROJECT"
author: "BASIC QUESTION"
date: "2024-04-18"
output: 
     prettydoc::html_pretty:
     themes: leonids
---
**Basic questions**


1.Create a vector called stock.prices with the following data points:
   23,27,23,21,34.
```{r}
stock_prices = c(23,27,23,21,34)
stock_prices
```

2.Create a numeric vector containing the numbers 1 to 10.
```{r}
numeric_vector = 1:10
numeric_vector
```

3.Calculate the sum of these numbers.
```{r}
sum(numeric_vector)
```

4.Create a logical vector indicating which numbers are even
```{r}
logical_vector = numeric_vector %% 2 == 0
logical_vector
```

5.Use the plot() function to create a scatter plot of the mtcars dataset, plotting mpg (miles per gallon) against hp (horsepower).
```{r}
library(ggplot2)
```

```{r}
data(mtcars)
head(mtcars)
```

```{r}

plot(mtcars$mpg,mtcars$hp,xlab = "MPG",ylab= "Hp",col="red",pch = 20,
     main = "Distribution of miles per gallon against horsepower")
```

6.Given a vector a = c("a", "b", "c", "d", "e"), extract the 2nd and 4th elements.

```{r}
 a = c("a", "b", "c", "d", "e")
 a
 a[c(2,4)]
```
7.From the mtcars dataset, select the rows where cyl (cylinders) is 4 and only the columns mpg, hp, and wt.

```{r}
library(dplyr)
```

```{r}
mtcars_data = select(filter(mtcars,cyl==4),'cyl','mpg','hp','wt')
mtcars_data
```
8.Create a list my_list that contains three elements: a numeric vector (1, 2, 3), a character vector (“a”, “b”, “c”), and a matrix with 2 rows and 2 columns.
```{r}
my_list = list(c(1,2,3),c('a','b','c'),matrix(1:4,nrow=2))
my_list
```

9.Add a new element to my_list that is a logical vector (TRUE, FALSE).
```{r}
my_list = c(my_list,'true','false')
my_list
```

10.Create character vector words with the elements “R”, “is”, “fun”.
```{r}
words = c('R','is','Fun')
words
```

11.Use a function to concatenate these words into a single string: “R is fun”.

```{r}
a = cat(words,"")

```
12.Replace “fun” with “awesome” in the concatenated string.

```{r}
a = 'r is fun'
b = gsub( 'fun','awsome',a)
b
```
13.From a numeric vector to a character vector: v_num = c(1, 2, 3)
```{r}
v_num = c(1, 2, 3)
typeof(v_num)
v_char = as.character(v_num)
v_char
typeof(v_char)
```
14.From a character vector to a factor: v_char = c("low", "medium", "high")
```{r}
v_char1 = c("low", "medium", "high")
c=as.factor(v_char1)
c
typeof(c)
```
15.From a factor to a numeric vector, considering the factor levels as numeric values: f = factor(c(1, 2, 3)).
```{r}
f = factor(c(1, 2, 3))
n= as.numeric(f)
n
typeof(n)
```
16.colors = c(“red”, “blue”, “green”, “blue”, “red”, “green”, “green”, “red”)

  1.Convert colors into a factor, f_colors.
```{r}
colors = c('red', 'blue', 'green', 'blue', 'red', 'green', 'green', 'red')
f_colors =factor(colors)
f_colors
```
  2.Print the levels of f_colors.
```{r}
f_colors
levels(f_colors)
```
 3.How would you reorder the levels of f_colors so that “green” comes first?
```{r}
colors = c('red', 'blue', 'green', 'blue', 'red', 'green', 'green', 'red')
f_colors =factor(colors,levels=c('green','blue','red'))
f_colors
```
17.my_list <- list(name = “Alice”, age = 30, hobbies = c(“Cycling”, “Art”, “Music”)) my_df <- data.frame(Name = c(“Alice”, “Bob”), Age = c(25, 30))

 1.Access and print the hobbies element from my_list.
```{r}
my_list = list(name = 'Alice', age = 30,
               hobbies = c('Cycling', 'Art', 'Music'))
my_list[[3]]
```

 2.Add a new column Occupation to my_df with values “Doctor” for Alice and “Engineer” for Bob.

```{r}
my_df = data.frame(Name = c('Alice', 'Bob'), Age = c(25, 30))
my_df = cbind(my_df,Occupation =c('doctor','Engineer'))
my_df
```

 
 
 
 