---
title: "R_PROJECT"
author: "STATEMENTS"
date: "2024-04-18"
output: 
      prettydoc::html_pretty:
         themes: leonids
---
**Statements Questions**

1.Write a script that will print “Even Number” if the variable x is an even number, otherwise print “Not Even”.
```{r}
x  = 4
if (x %% 2 == 0) {
  print("Even Number")
} else {
  print("Not Even")
}
```
2.Write a script that will print ‘Is a Matrix’ if the variable x is a matrix, otherwise print “Not a Matrix”. Hint: You may want to check out help(is.matrix)

```{r}
x = matrix(1:4, ncol=2)
if (is.matrix(x)) {
  print("Is a Matrix")
} else {
  print("Not a Matrix")
}
```

3.Create a script that given a numeric vector x x=c(3,7,1), will print out the elements in order from high to low i.e (1,3,7). You must use if,else if, and else statements for your logic.

```{r}
x = c(3,7,1)
if (x[1] > x[2] & x[1] > x[3]) {
  if (x[2] > x[3]) {
    print(c(x[3], x[2], x[1]))
  } else {
    print(c(x[2], x[3], x[1]))
  }
} else if (x[2] > x[1] & x[2] > x[3]) {
  if (x[1] > x[3]) {
    print(c(x[3], x[1], x[2]))
  } else {
    print(c(x[1], x[3], x[2]))
  }
} else {
  if (x[1] > x[2]) {
    print(c(x[2], x[1], x[3]))
  } else {
    print(c(x[1], x[2], x[3]))
  }
}
```


4.Write a script that uses if,else if, and else statements to print the max element in a numeric vector with 3 elements.
Ex. x = c(3,7,1) 7 should be the output
```{r}
x = c(3,7,1)
if (x[1] > x[2] & x[1] > x[3]) {
  print(x[1])
} else if (x[2] > x[1] & x[2] > x[3]) {
  print(x[2])
} else {
  print(x[3])
}
```

