---
title: "R_PROJECT"
author: "DATA FRAMES"
date: "2024-04-18"
output: 
    prettydoc::html_pretty:
     themes: leonids
---
**DATA FRAME QUESTION**
```{r }
library(dplyr)
```


1.Create a data frame named df_students with the following columns: ID, Name, Age, and Grade. Populate it with data for 5 students. Perform the following operations:

```{r}
df_students =data.frame(ID = c(1,2,3,4,5),
                       Name= c('sun','moon','earth','mars','jupter') ,
                        Age= c(23,24,17,18,20),
                        Grade = c('90','80','50','60','40')
                        )
df_students
```


1.1.Add a new column Passed that indicates with TRUE or FALSE whether each student passed (assume a passing grade is at least 60).
```{r}
df_stud = mutate(df_students,Passed = Grade >= 60)
df_stud
```


1.2.Select and print only the rows of students who are 18 years or older.
```{r}
dt=select(filter(df_students,Age>=18),'ID','Name','Age','Grade')
dt
```

2.Suppose you have two data frames, df_A and df_B. df_A contains student IDs and names, while df_B contains student IDs and their corresponding courses. Write R code to merge these data frames so each row contains a student’s ID, name, and course.
```{r}
df_A =data.frame(stud_id = c(1:5),
                 name = c('alice','peter','john','ferry','jenny'))
df_A
```

```{r}
df_B =data.frame(stud_id = c(1:5),
                 courses = c('maths','english','physis','chemistry','computer'))
df_B
```

```{r}
new_df =merge(df_A,df_B,by ='stud_id')
new_df
```
3.Given a data frame df_sales with columns Date, ProductID, Quantity, and Price, write R code to calculate the total sales (Quantity * Price) for each product.

 1.Note: Generate your own data set.
```{r}

df_sales = data.frame(Date =c('2024-01-10','2024-01-20','2024-02-15','2024-02-25','2024-03-30'),
                      ProductID = c(1:5),
                      Quantity = c(10,20,30,40,50),
                      Price = c(1000,1500,2000,2500,3000))
df_sales
```
```{r}
df_sales %>%
  group_by(ProductID) %>%
  summarise(total_sales = sum(Quantity * Price))
```

**4.For iris data set.**

4.1.Calculate the average Sepal.Length for each Species.

```{r}
data(iris)
head(iris)
```

```{r}
data =aggregate(Sepal.Length ~ Species,iris,mean)
data
```

4.2.Create a new column Sepal.Area which is the product of Sepal.Length and Sepal.Width.
```{r}
new =mutate(iris,Sepal_Area = iris$Sepal.Length *iris$Sepal.Width)
new
```

4.3.Find the species with the highest average Sepal.Area.
```{r}
iris %>%
  mutate(Sepal.Area = Sepal.Length * Sepal.Width) %>%
  group_by(Species) %>%
  summarise(mean_Sepal_Area = mean(Sepal.Area)) %>%
  arrange(desc(mean_Sepal_Area)) %>%
  head(1)
```

**5.For airquality data set.**
```{r}
data(airquality)
head(airquality)
```

```{r}
names(airquality)
```

5.1.Calculate the average Ozone level for each month, excluding missing values.
```{r}
a= airquality %>%
    group_by(Month) %>%
    summarise(ozone_mean_data = mean(Ozone,na.rm = TRUE))
a
```

5.2.Determine the month with the highest average Ozone level.
```{r}
airquality %>%
group_by(Month) %>%
summarise(ozone_mean_data = mean(Ozone,na.rm = TRUE)) %>%
arrange(desc(ozone_mean_data)) %>%
head(1)
```

5.3.Create a new data frame with Month and Temp columns, excluding days with missing Ozone values.
```{r}
air = select(filter(airquality, !is.na(Ozone)), Month, Temp)
air
```



