---
title: "R_PROJECT"
author: "GGPLOT"
date: "2024-04-18"
output: 
   prettydoc::html_pretty:
     themes: leonids
       
---
**GGPLOT Questions**

**USE mtcars default data**

1.Histogram of hwy mpg values.

```{r}
library(ggplot2)
```

```{r}
data(mtcars)
head(mtcars)
```
```{r}


ggplot(mtcars,aes (x = mpg) ) + geom_histogram(color="darkblue",
            fill="lightblue")
```

2.Barplot of car counts per manufacturer with color fill defined by cyl count.

```{r}
a = row.names(mtcars)
a
```

```{r}
ggplot(mtcars,aes(x=a,fill =cyl))+geom_bar()+ theme(axis.text.x = element_text(face="bold", color="#993333", size=14, angle=90))
```

3.Switch now to use the txhousing dataset that comes with ggplot2.

```{r}

data( txhousing )
 head(txhousing)
```

4.Create a scatterplot of volume versus sales. Afterwards play around with alpha and color arguments to clarify information.

```{r}

x =txhousing$volume
y =txhousing$sales
plot(x,y, xlab ='volume',ylab ='sales',main ='scatterplot of volume Vs sales',col ='purple',pch =20 )+geom_point(alpha=0.6)
```

5.Add a smooth fit line to the scatterplot from above. Hint: You may need to look up geom_smooth().
```{r}

ggplot(txhousing, aes(x =volume,y = sales,na.rm = TRUE))+geom_point(col =' purple',
alpha=0.6,na.rm = TRUE)+ggtitle("Scatterplot of volume Vs sales")+
  theme(plot.title = element_text(size =rel(2.0),face="bold",hjust =0.5,color ='red'))+geom_smooth(na.rm = TRUE)
```

**USE airquality default data**

1.The x-axis represents the Day of the month.

2.The y-axis represents the Ozone levels.

3.Color the points by Month.

4.Add a smooth trend line to the plot.
```{r}
data(airquality)
head(airquality)
```

```{r}

ggplot(airquality, aes(x=Ozone, y=Day,fill =factor(Month),na.rm =TRUE))+geom_smooth(method = 'loess',na.rm =TRUE,formula = 'y ~ x')
```

**USE checkweight default data**

1.Plots Time on the x-axis and weight on the y-axis.

2.Uses different colors to represent each Diet.

3.Groups the lines by Chick to show individual growth trajectories within each diet.
```{r}

data(ChickWeight)
head(ChickWeight)
```
```{r}

ggplot(ChickWeight, aes(x =Time,y =weight,colour=Diet, group=Chick))+geom_line()
```

**USE diamonds default data**

Create a histogram to show the distribution of carat sizes. Then, refine your plot by:

1.Filling the bars based on the cut quality of the diamonds.

2.Limiting the x-axis to diamonds up to 3 carats for better detail.

```{r}

data(diamonds)

```
```{r}

head (diamonds)
```

```{r}

ggplot(diamonds, aes(x =carat ,fill = cut,na.rm =TRUE))+geom_histogram(bins = 10,na.rm =TRUE)+ xlim(0, 3)
```




